Radio Emission from Red-Giant Hot Jupiters

### 2015-09-16 ms.tex
Note on number of electrons ... See the memo below eq. 18

The source rate is obtained by counting the number of photons whose energy exceeds the ionization energy of Hydrogen ($E_{\rm Rydberg} = 13.6$~eV, %where Ry is the Rydberg constant, 
or $\lambda = 91.2\rm~nm$), which is approximately given by dividing the X-ray accretion luminosity by the characteristic photon energy produced:
%%%%%%%%%
\begin{equation}
\dot{N}_X \sim \frac{L_{\rm acc}}{k_B T_{\rm acc}} \, ,
\end{equation}
%%%%%%%%%
where $k_B$ is Boltzmann's constant.
As a result, 
%%%%%%%%%
\begin{eqnarray}
\dot{N}_X \sim  
  \left\{
    \begin{array}{ll}
      2 \times 10^{35} \;  {\rm sec^{-1}} & \;\;\;(M_p = M_J) \\
      3 \times 10^{37} \; {\rm sec^{-1}} & \;\;\;(M_p = 10 M_J)
    \end{array}. 
  \right.
\end{eqnarray}
%%%%%%%%%
For the accretion disks of large planets, however, the characteristic photon energy is so high (equation (\ref{eq:Tacc})) that the released energetic electrons may also ionize other atoms in the vicinity; the cross section of hydrogen for electrons is $\sim 4\times 10^{-17} {\rm cm}^2$  \citep{fite1958} and thus about 60\% of the released electrons will be used to ionize other atoms within a distance of $2R_J$. 
In theory, photons with energy $E{\rm photon}$ have potential to ionize $E_{\rm photon}/E_{\rm Rydberg}$ times. 
To take this into account, we also consider replacing the source term $\dot N_X$ in equation (\ref{eq:equilibrium}) by 
%%%%%%%%%
\begin{equation}
\dot{N}_X \rightarrow \dot{N}_X \left[ 1 + f \left( \frac{E_{\rm photon}}{E_{\rm Rydberg}} - 1 \right) \right] 
\end{equation}
%%%%%%%%%
where the $f$ is a fudge factor to represent the efficiency of this reaction.

The ionization fraction $x$ as a solution of equation (\ref{eq:equilibrium}) is shown in Figure \ref{fig:ionizationfraction}. 
The solid lines show the ionization fraction of $f=0$ (no additional ionization by electrons) and dashed lines show that of $f=0.5$. In the figure, the vertical lines show the magnetic stand-off points obtained by equation (\ref{eq:stand-off-radius}) below. \memoYF{need to replace the order?} 
While the photon rate is large for larger planets, the strong dependence of cross section on the photon energy (equation \ref{eq:sigma_H}) leads to the decrease in the radius of ionized region. 
Nevertheless, still, substantial amount of ionized plasmas are expected around the magnetic stand-off radius.

>>>>

The source rate is obtained by counting the number of photons whose energy exceeds the ionization energy of Hydrogen ($E_{\rm Rydberg} = 13.6$~eV, %where Ry is the Rydberg constant, 
or $\lambda = 91.2\rm~nm$), which is approximately given by dividing the X-ray accretion luminosity by the characteristic photon energy produced:
%%%%%%%%%
\begin{equation}
\dot{N}_X \sim \frac{L_{\rm acc}}{k_B T_{\rm acc}} \, ,
\end{equation}
%%%%%%%%%
where $k_B$ is Boltzmann's constant.
As a result, 
%%%%%%%%%
\begin{eqnarray}
\dot{N}_X \sim  
  \left\{
    \begin{array}{ll}
      2 \times 10^{35} \;  {\rm sec^{-1}} & \;\;\;(M_p = M_J) \\
      3 \times 10^{37} \; {\rm sec^{-1}} & \;\;\;(M_p = 10 M_J)
    \end{array}. 
  \right.
\end{eqnarray}
%%%%%%%%%
For the accretion disks of large planets, however, the characteristic photon energy is so high (equation (\ref{eq:Tacc})) that the released energetic electrons may also ionize other atoms in the vicinity; the cross section of hydrogen for electrons is $\sim 4\times 10^{-17} {\rm cm}^2$  \citep{fite1958} and thus about 60\% of the released electrons will be used to ionize other atoms within a distance of $2R_J$. 
Photons with energy $E{\rm photon}$ have potential to ionize $E_{\rm photon}/E_{\rm Rydberg}$ times. 
To take this into account, we also consider replacing the source term $\dot N_X$ in equation (\ref{eq:equilibrium}) by 
%%%%%%%%%
\begin{equation}
\dot{N}_X \rightarrow \dot{N}_X \left[ 1 + \xi \left( \frac{E_{\rm photon}}{E_{\rm Rydberg}} - 1 \right) \right] 
\end{equation}
%%%%%%%%%
where the $\xi$ is a fudge factor to represent the efficiency of this reaction. \memoDS{Does the above argument imply that $\xi \sim 0.6$?  Should we think of it as an $N$-Rydberg photon, if absorbed, leads to 1 $N-1$-Rydberg electron, which produces 0.6 $N-2$-Rydberg electrons, $0.6^2$ $N-3$-Rydberg electrons, ... and $0.6^{N-1}$ 0-Rydberg electrons, so in the end we have $1 + 0.6 + 0.6^2 + ... + 0.6^{N-1} \sim 2.5$ electrons?}
% N - power - 1 = energy of electrons
% N - (N-1) - 1 = 0-Rydberg electron

The ionization fraction $x$ as a solution of equation (\ref{eq:equilibrium}) is shown in Figure \ref{fig:ionizationfraction}. \memoDS{We should write the expression ... it's just the quadratic formula, but it would be useful to write.}
The solid lines show the ionization fraction of $f=0$ (no additional ionization by electrons) and dashed lines show that of $f=0.5$. In the figure, the vertical lines show the magnetic stand-off points obtained by equation (\ref{eq:stand-off-radius}) below. \memoYF{need to replace the order?} 
While the photon rate is large for larger planets, the strong dependence of cross section on the photon energy (equation \ref{eq:sigma_H}) leads to the decrease in the radius of ionized region. 
Nevertheless, still, substantial amount of ionized plasmas are expected around the magnetic stand-off radius.
